How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-22 docs/PhysicsPaper/StokesErosion.tex
NM

	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}. Though the governing fluid-flow equations (Stokes) in this regime are linear, the feedback between complex eroding geometries and the flow leads to highly nonlinear behavior.

	Figure \ref{fig1} shows an example simulation of the erosion of 80 bodies, with the local speed of the intervening fluid flow shown by color. This simulation illustrates the {\em channelization} process, in which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels. The positive feedback creates the channels that are clearly visible by in final two images.

%\ref{fig1}

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}%[htbp]
\centering \label{fig1}
\includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
\caption{Numerical simulation of a dense suspension of 80 bodies eroding in a Stokes flow.
Over time, the non-uniform erosion of material opens channels in the medium, leading to high anisotropy.}
\end{figure*}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

>>>>

	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}. Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.

	Figure \ref{fig1} shows an example simulation in which 80 circular bodies of randomized sizes and positions are immersed in a Stokes flow that moves from left to right. Color depicts the local speed of the flow intervening between bodies to give a sense of where the flow is strongest. Over time, individual bodies erode in response to the shear stresses induced on them.
The heterogeneous material removal creates visible features both at the level of individual bodies and the larger-scale configuration. For example, horizontally-oriented channels are clearly visible in the third and fourth frames.

%which regions of high flow speed create higher local shear rates, thus preferentially removing solid material, and further opening the channels. The positive feedback creates the channels that are clearly visible by in final two images.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure*}%[htbp]
\centering \label{fig1}
\includegraphics[width = 0.99 \textwidth]{./figs/Velocity-80-4.pdf}
\caption{The erosion of a porous medium. In this simulation, an initial configuration of 80 circular bodies of randomized sizes and positions are embedded in a Stokes flow that moves from left to right. The figure shows four snapshots, evenly spaced in time, as the bodies erode in response to the local shear stresses induced by the flow. The local flow speed, shown by color, highlights the appearance of horizontally-aligned channels created by the shape-flow feedback. These channels contribute to the high anisotropy of the medium.
}
\end{figure*}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Times are 0, 0.28, 0.57, 0.85 of final time.
% Porosities are 0.40, 0.49, 0.64, 0.86.
